Detecting threats of violence in YouTube comments

### 2016-02-15 submission.tex
Added experimental setup

@@

\section{Introduction}
\label{sec:intro}
Threats of violence is an increasingly common occurrence in online
discussions. It disproportionally affects women and minorities, often
to the point of effectively eliminating them from taking part in
discussions online. Moderators of social networks operate on such a
large scale that manually reading all posts is an insurmountable
task. Methods for automatically detecting threats could therefore
potentially be very helpful, both to moderators of social networks,
and to the members of those networks.

@@

The data set consists of 9,845 comments, comprised of 28,643
sentences, see table \ref{tab:dataset}. In total there are 402,673
tokens in the sentences in the data set. There are 1,285 comments
containing threats, and 1,384 sentences containing threats, as seen in
table \ref{tab:dataset}.  \cite{hammer2014} report inter annotator
agreement on this data set to be 98~\%, as calculated on 120 of the
comments, doubly annotated for evaluation.

@@

\begin{figure*}[h]
\begin{verbatim}
timpa666
1    and i will kill every fucking muslim and arab!

@@

\subsection{Experimental setup}
%% todo:
%% - data split
%% - preprocessing
%% - machine learner
%% - tuning
%% - feature templates

@@

%\subsection{Error analysis}

%\subsection{Held-out results}

\section{Discussion}
\label{sec:disc}

>>>>

\usepackage{pgfplots}
% Anbefalt her: https://www.sharelatex.com/learn/Pgfplots_package#Introduction
\pgfplotsset{width=10cm}

@@

\section{Introduction}
\label{sec:intro}
Threats of violence constitute an increasingly common occurrence in online
discussions. It disproportionally affects women and minorities, often
to the point of effectively eliminating them from taking part in
discussions online. Moderators of social networks operate on such a
large scale that manually reading all posts is an insurmountable
task. Methods for automatically detecting threats could therefore
potentially be very helpful, both to moderators of social networks,
and to the members of those networks.

@@

The data set consists of 9,845 comments, comprised of 28,643
sentences, see table \ref{tab:dataset}. In total there are 402,673
tokens in the sentences in the data set. There are 1,285 comments
containing threats, and 1,384 sentences containing threats, as seen in
table \ref{tab:dataset}.  \newcite{hammer2014} report inter annotator
agreement on this data set to be 98~\%, as calculated on 120 of the
comments, doubly annotated for evaluation.

@@

\begin{figure*}
\begin{verbatim}
timpa666
1    and i will kill every fucking muslim and arab!

@@

\subsection{Experimental setup}
The data set is split into an 80-20 training and testing set. All
tuning and development experiments were performed using 10-fold
cross-validation on the training set.

Since threat annotation is performed on the sentence level, the data
set has been manually split into sentences as part of the annotation
process.  We performed tokenization, lemmatization, PoS-tagging and
dependency parsing using the spaCy toolkit REF.  SpaCy assigns both
the standard Penn Treebank PoS-tags REF, as well as the more
coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
dependency parser assigns an analysis in compliance with the ClearNLP
converter REF. The data set was further enriched with the cluster
labels described in Turian et al.~\shortcite{Tur:Rat:Ben:10}, created
using the Brown clustering algorithm \cite{Bro:deS:Mer:92} and induced
from the RCV1 corpus, a corpus containing Reuters English newswire
text, with approximately 63 million words and 3.3 million sentences.
WordNet REF

%% todo:
%% - data split
%% - preprocessing
%%   Spacy, Brown clusters, WordNet
%% - machine learner
%% - tuning
%% - feature templates

@@

\subsection{Error analysis}

\subsection{Held-out results}

\section{Conclusion}
\label{sec:disc}
